Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-16 robdml.tex
tex

It \emph{should} be noted that the $L_\text{ICS}$ term improves 
robustness against most attacks involved in ERS, but also increases the
tendency to collapse (observed from the score for TMA~\cite{flowertower} --
high cosine similarity between two arbitrary benign examples).
%
In some cases (\eg, on SOP), the performance drop \emph{w.r.t} TMA may
neutralize the ERS gain from other attacks.

@@

Further discussions, technical details, and limitations, \etc,
are presented in the supplementary document.

>>>>

It \emph{should} be noted that the $L_\text{ICS}$ term improves 
robustness against most attacks involved in ERS, but also increases the
tendency to collapse (observed during TMA~\cite{flowertower} attack --
high cosine similarity between two arbitrary benign examples).
%
In some cases (\eg, on SOP), the performance drop \emph{w.r.t} TMA may
neutralize the ERS gain from other attacks.

@@

Further analysis, technical details, and limitations, \etc,
are presented in the supplementary document.
